Causal.jl:\\A Modeling and Simulation Framework for Causal Models

### 2021-12-05 paper/paper.tex
Added doi.

In Causal.jl, it is possible to simulate models that include components represented by different types of equations. In Figure \ref{fig: coupled model} is given such an example model. \texttt{odeds} is a dynamical system represented by the ordinary differential equation in (\ref{eq: coupled ode}) where where $x_1, y_1, z_1$ are the state variables and $a=35, b=3, c = 28$ are system parameters.
\begin{equation}
    \begin{split}
        \dot{x}_1 &= a (y_1 - x_1) \\
        \dot{y}_1 &= (c - 1) x_1 + c y_1 - x_1 z_1 \\
        \dot{z}_1 &= x_1 y_1 - b z_1
    \end{split}
    \label{eq: coupled ode}
\end{equation}
\texttt{sdeds} is dynamical system that is represented by the stochastic differential equation in (\ref{eq: coupled sde}) where $x_2, y_2, z_2$ are the state variables, $u=[u_1,u_2, u_3]$ is the input, $\eta$ is noise strength, $W_t$ is the Wiener process corresponding to the noise and $a, b, c$ are the same as those in (\ref{eq: coupled ode}).
\begin{equation}
    \begin{split}
        dx_2 &= (a (y_1 - x_1) + u_1) dt + \eta dW_t \\
        dy_2 &= ((c - 1) x_1 + c y_1 - x_1 z_1)dt + \eta dW_t \\
        dz_2 &= (x_1 y_1 - b z_1 + u_3) dt + \eta dW_t 
    \end{split}
    \label{eq: coupled sde}
\end{equation}
\texttt{gain} is a static system whose input output relation is given in (\ref{eq: gain}) where $u, y, \epsilon$ are the input, output and gain coefficient of the system. 
\begin{equation}
    y = \epsilon u
    \label{eq: gain}
\end{equation}
\texttt{writer1} and \texttt{writer2} are used to record the outputs of \texttt{odeds} and \texttt{sdeds}, respectively, while \texttt{writer3} is used to record the fast Fourier transform (FFT) of the data flowing out of \texttt{odeds}\cite{proakis2004digital}.

>>>>

In Causal.jl, it is possible to simulate models that include components represented by different types of equations. In Figure \ref{fig: coupled model} is given such an example model. \texttt{odeds} is a dynamical system represented by the ordinary differential equation in (\ref{eq: coupled ode}) where where $x_1, y_1, z_1$ are the state variables and $a=35, b=3, c = 28$ are system parameters.
\begin{equation}
    \begin{split}
        \dot{x}_1 &= a (y_1 - x_1) \\
        \dot{y}_1 &= (c - 1) x_1 + c y_1 - x_1 z_1 \\
        \dot{z}_1 &= x_1 y_1 - b z_1
    \end{split}
    \label{eq: coupled ode}
\end{equation}
\texttt{sdeds} is dynamical system that is represented by the stochastic differential equation in (\ref{eq: coupled sde}) where $x_2, y_2, z_2$ are the state variables, $u=[u_1,u_2, u_3]$ is the input, $\eta$ is noise strength, $W_t$ is the Wiener process corresponding to the noise and $a, b, c$ are the same as those in (\ref{eq: coupled ode}).
\begin{equation}
    \begin{split}
        dx_2 &= (a (y_1 - x_1) + u_1) dt + \eta dW_t \\
        dy_2 &= ((c - 1) x_1 + c y_1 - x_1 z_1)dt + \eta dW_t \\
        dz_2 &= (x_1 y_1 - b z_1 + u_3) dt + \eta dW_t
    \end{split}
    \label{eq: coupled sde}
\end{equation}
\texttt{gain} is a static system whose input output relation is given in (\ref{eq: gain}) where $u, y, \epsilon$ are the input, output and gain coefficient of the system.
\begin{equation}
    y = \epsilon u
    \label{eq: gain}
\end{equation}
\texttt{writer1} and \texttt{writer2} are used to record the outputs of \texttt{odeds} and \texttt{sdeds}, respectively, while \texttt{writer3} is used to record the fast Fourier transform (FFT) of the data flowing out of \texttt{odeds}\cite{proakis2001digital}.
